Carrier phase and amplitude estimation of $M$-ary phase shift keying using pilots and data

### 2012-05-22 paper.tex
Added a bunch of new data files.  Added a bit more to the paper.

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. If $g(\phi)$ is continuous at $\phi = (2k+1)\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = \frac{1}{(p + H d)^2} \left( \begin{array}{cc} 
pA_1 + dA_2 & ? \\
? & ?
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}),
\]
\[
A_1 = \expect R_1^2\sin^2(\Phi_1), \qquad A_2 = \expect R_1^2\sin^2\fracpart{\Phi_1}.
\]
\end{theorem}

@@

We first prove the asymptotic normality of $\sqrt{L} \hat{\lambda}_L$.  Once this is done we will be able to prove the normality of $\sqrt{L} m_L$.  Recall that $\hat{\lambda}_L$ is the maximiser of the function $G_L$ defined in~\eqref{eq:GLdefn}.  The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at multiples of $\tfrac{\pi}{M}$.  This prevents the use of ``standard approaches'' to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989}.  However, we show in Lemma~\ref{lem:diffatlambdaL} that the derivative $G_L^\prime$ does exist, and is equal to zero, at the maximiser $\hat{\lambda}_L$, so
\begin{align*}
G_L^\prime(\hat{\lambda}_L) &= 0 \\
&= \frac{1}{L} \sum_{i \in P} R_i \sin(\hat{\lambda}_L + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\hat{\lambda}_L + \Phi_i}.
\end{align*}
Define the function $Q(\lambda) = \expect G_L^\prime(\lambda) - \expect G_L^\prime(0)$ and write
\begin{align*}
0 &= G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) + Q(\hat{\lambda}_L) \\
&= \sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) + \sqrt{L}Q(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $o_P(1)$ denotes a number converging in probablity to zero as $L \rightarrow \infty$.  The constant real numbers $p,d$ and $H$ are defined in the statement of Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
It follows from the three equations above that,
\[
0 = o_P(1) + \sqrt{L}G_L^\prime(0) + \sqrt{L} \hat{\lambda}_L \big( p + Hd  + o_P(1) \big)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L = o_P(1) + \frac{\sqrt{L}G_L'(0)}{p + Hd  + o_P(1)}.
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$ where $A_1$ and $A_2$ are real constants defined in the statement of Thereom~\ref{thm:normality}.  It follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{pA_1 + dA_2}{(p + Hd)^2}.
\]

We now analyse the asymptotic distribution of $\sqrt{L} m_L$.  Define the function $T(\lambda) = \expect G_L(\lambda)$.  Using~\eqref{eq:rhoGLZ},
\begin{align*}
\sqrt{L} m_L &= \sqrt{L} \rho_0 \big( G_L(\hat{\lambda}_L) - G(0) \big) \\
&= \sqrt{L} \rho_0 \big( G_L(\hat{\lambda}_L) - T(\hat{\lambda}_L) + T(\hat{\lambda}_L) - G(0) \big).
\end{align*}
Lemma~\ref{lem:empiricprocforrho} shows that 
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T(\hat{\lambda}_L)  \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L}\big( G_L(0) - T(0)  \big)$.  Lemma~\ref{lem:HLtoG} shows that
\[
\sqrt{L}\big( T(\hat{\lambda}_L) - G(0) \big) = \sqrt{L} \hat{\lambda}_L \big( ? + o_P(1) \big).
\]
It follows that
\[
\sqrt{L} m_L = o_P(1) + X_L  + \hat{\lambda}_L \big( ? + o_P(1) \big).
\]
Lemma~\ref{lem:XL} shows that the distrubtion of $X_L$ converges to the normal with zero mean and variance
\[
?
\]
and Lemma~\ref{lem:XLcovlambdaL} shows that the covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ goes to zero as $L\rightarrow\infty$.  So, the distribution of $\sqrt{L}m_L$ converges to the normal with zero mean and variance
\[
\var X_L + \var \sqrt{L} \hat{\lambda}_L ?^2 = BLERG.
\]
The covariance between $\sqrt{L}m_L$ and $\sqrt{L}\hat{\lambda}_L$ is correspondingly
\[
?
\]
It remains to prove the lemmas that we have used.

@@

\begin{lemma}\label{lem:Qconv}
$\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)$
\end{lemma}
\begin{IEEEproof}
We have
\[
Q(\lambda) = \expect G_L^\prime(\lambda) - \expect G_L^\prime(0) = \tfrac{\abs{P}}{L} k_1(\lambda) + \tfrac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align}
k_1(\lambda) &= \expect R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \nonumber\\
k_2(\lambda) &= \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big). \label{eq:k2def}
\end{align}
We analyse $k_1(\lambda)$ first.  By a Taylor expansion of $\sin(\lambda + \Phi_1)$ about $\Phi_1$ we obtain
\[
\sin(\lambda + \Phi_1) - \sin(\Phi_1) = \lambda \big( \cos(\Phi_1) + \zeta(\lambda) \big),
\]
where $\zeta(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero.  Then,
\begin{align*}
k_1(\lambda) &= \expect R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \expect R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \expect R_1 \big) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) K \big),
\end{align*}
since $h_1(0) = \expect R_1\cos(\Phi_1) = 1$ because $w_1$ is circularly symmetric, and $K = \expect R_1$ is a finite constant because $\expect\abs{w_1}$ is finite (by assumption in Theorem~\ref{thm:consistency}).  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) K \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big).
\]
Lemma~\ref{lem:k2conv} shows that $k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) )$.  So,
\begin{align*}
Q(\hat{\lambda}_L) &=  \tfrac{\abs{P}}{L} \hat{\lambda}_L \big( 1  + o_P(1)\big)  + \tfrac{\abs{D}}{L} \hat{\lambda}_L ( H + o_P(1) ) \\
&= \hat{\lambda}_L \left( \tfrac{\abs{P}}{L}  + \tfrac{\abs{D}}{L} H + o_P(1) \right).
\end{align*}
The proof follows since $\frac{\abs{P}}{L} \rightarrow p$ and $\frac{\abs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:k2conv}
$k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) ).$
\end{lemma}
\begin{IEEEproof}
Since $\hat{\lambda}_L \in [-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ it is only the behaviour of the function $k_2(\lambda)$ for $\lambda\in [-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ that is relevant.  We will analyse $k_2(\lambda)$ for non negative $\lambda$, i.e., when $0 \leq \lambda < \tfrac{\pi}{M}$.  An analagous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  To keep our notation clean put
\[
\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}.
\]
For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_k)$, then
\[
\fracpart{\Phi_1} = \Phi_1 - \round{\Phi_1} = \Phi_1 - \tfrac{2\pi}{M}k.
\]
Similarly, if $\Phi_1 \in  [\psi_{k-1}, \psi_{k} - \lambda)$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k,
\]
whilst, if $\Phi_1 \in [\psi_{k} - \lambda, \psi_{k})$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}.
\]
So, when $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - &\sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k)$ about $\Phi_1 - \tfrac{2\pi}{M}k$ we obtain 
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} &= \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k) + \zeta_k(\lambda)\big) \\
&= \lambda\big(\cos\fracpart{\Phi_1} + \zeta_k(\lambda)\big).
\end{align*}
where $\zeta_k(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero.  Alternatively, when $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} &- \sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k)
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M})$ about $\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}$,
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&=  s_k(\Phi_1) + \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) + \zeta_{k+1}(\lambda)\big) 
\end{align*}
where
\[
s_k(\Phi_1) = \sin(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k).
\]
Putting,
\[
c_k(\Phi_1) = \cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \cos(\Phi_1 - \tfrac{2\pi k}{M})
\]
we can write
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&= s_k(\Phi_1) + \lambda\big(\cos(\Phi_1 - \tfrac{2\pi k}{M}) + c_k(\Phi_1) + \zeta_{k+1}(\lambda)\big) \\
&= s_k(\Phi_1) + \lambda\big(\cos\fracpart{\Phi_1} + \eta_k(\lambda, \Phi_1) \big).
\end{align*}
where, for convenience, we put $\eta_k(\lambda, \Phi_1) = c_k(\Phi_1) + \zeta_{k+1}(\lambda)$.  Observe that both $s_k$ and $c_k$ are continuous functions and that $s_k(\psi_{k}) = -2\sin(\tfrac{\pi}{M})$ and $c_k(\psi_{k}) = 0$.

>>>>

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. %If $g(\phi)$ is continuous at $\phi = (2k+1)\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, Then 
Then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = \frac{1}{(p + H d)^2} \left( \begin{array}{cc} 
pA_1 + dA_2 & ? \\
? & ?
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}),
\]
\[
A_1 = \expect R_1^2\sin^2(\Phi_1), \qquad A_2 = \expect R_1^2\sin^2\fracpart{\Phi_1}.
\]
\end{theorem}

@@

We first prove the asymptotic normality of $\sqrt{L} \hat{\lambda}_L$.  Once this is done we will be able to prove the normality of $\sqrt{L} m_L$.  Recall that $\hat{\lambda}_L$ is the maximiser of the function $G_L$ defined in~\eqref{eq:GLdefn}.  The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at multiples of $\tfrac{\pi}{M}$.  This prevents the use of ``standard approaches'' to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989}.  However, we show in Lemma~\ref{lem:diffatlambdaL} that the derivative $G_L^\prime$ does exist, and is equal to zero, at the maximiser $\hat{\lambda}_L$, so
\begin{align*}
G_L^\prime(\hat{\lambda}_L) &= 0 \\
&= \frac{1}{L} \sum_{i \in P} R_i \sin(\hat{\lambda}_L + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\hat{\lambda}_L + \Phi_i}.
\end{align*}
Define the function $Q(\lambda) = \expect G_L^\prime(\lambda) - \expect G_L^\prime(0)$ and write
\begin{align*}
0 &= G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) + Q(\hat{\lambda}_L) \\
&= \sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) + \sqrt{L}Q(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $o_P(1)$ denotes a number converging in probablity to zero as $L \rightarrow \infty$.  The constant real numbers $p,d$ and $H$ are defined in the statement of Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
It follows from the three equations above that,
\[
0 = o_P(1) + \sqrt{L}G_L^\prime(0) + \sqrt{L} \hat{\lambda}_L \big( p + Hd  + o_P(1) \big)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L = o_P(1) - \frac{\sqrt{L}G_L'(0)}{p + Hd  + o_P(1)}.
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$ where $A_1$ and $A_2$ are real constants defined in the statement of Thereom~\ref{thm:normality}.  It follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{pA_1 + dA_2}{(p + Hd)^2}.
\]

We now analyse the asymptotic distribution of $\sqrt{L} m_L$.  Define the function $T(\lambda) = \expect G_L(\lambda)$.  Using~\eqref{eq:rhoGLZ},
\begin{align*}
\sqrt{L} m_L &= \sqrt{L} \rho_0 \big( G_L(\hat{\lambda}_L) - G(0) \big) \\
&= \sqrt{L} \rho_0 \big( G_L(\hat{\lambda}_L) - T(\hat{\lambda}_L) + T(\hat{\lambda}_L) - G(0) \big).
\end{align*}
Lemma~\ref{lem:empiricprocforrho} shows that 
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T(\hat{\lambda}_L)  \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L}\big( G_L(0) - T(0)  \big)$.  Lemma~\ref{lem:HLtoG} shows that
\[
\sqrt{L}\big( T(\hat{\lambda}_L) - G(0) \big) = \sqrt{L} \hat{\lambda}_L \big( ? + o_P(1) \big).
\]
It follows that
\[
\sqrt{L} m_L = o_P(1) + X_L  + \hat{\lambda}_L \big( ? + o_P(1) \big).
\]
Lemma~\ref{lem:XL} shows that the distrubtion of $X_L$ converges to the normal with zero mean and variance
\[
?
\]
and Lemma~\ref{lem:XLcovlambdaL} shows that the covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ goes to zero as $L\rightarrow\infty$.  So, the distribution of $\sqrt{L}m_L$ converges to the normal with zero mean and variance
\[
\var X_L + \var \sqrt{L} \hat{\lambda}_L ?^2 = ?.
\]
The covariance between $\sqrt{L}m_L$ and $\sqrt{L}\hat{\lambda}_L$ is correspondingly
\[
?
\]
It remains to prove the lemmas that we have used.

@@

\begin{lemma}\label{lem:Qconv}
$\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)$
\end{lemma}
\begin{IEEEproof}
We have
\[
Q(\lambda) = \expect G_L^\prime(\lambda) - \expect G_L^\prime(0) = \tfrac{\abs{P}}{L} k_1(\lambda) + \tfrac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align}
k_1(\lambda) &= \expect R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \nonumber\\
k_2(\lambda) &= \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big). \label{eq:k2def}
\end{align}
We analyse $k_1(\lambda)$ first.  By a Taylor expansion of $\sin(\lambda + \Phi_1)$ about $\Phi_1$ we obtain
\[
\sin(\lambda + \Phi_1) - \sin(\Phi_1) = \lambda \big( \cos(\Phi_1) + \zeta(\lambda) \big),
\]
where $\zeta$ is a continuous function with $\zeta(0) = 0$.  So,
\begin{align*}
k_1(\lambda) &= \expect R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \expect R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \expect R_1 \big) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) K \big),
\end{align*}
since $h_1(0) = \expect R_1\cos(\Phi_1) = 1$ because $w_1$ is circularly symmetric, and $K = \expect R_1$ is a finite constant because $\expect\abs{w_1}$ is finite (by assumption in Theorem~\ref{thm:consistency}).  Because $\zeta$ with $\zeta(0) = 0$ and because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) K \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big).
\]
Lemma~\ref{lem:k2conv} shows that $k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) )$.  So,
\begin{align*}
Q(\hat{\lambda}_L) &=  \tfrac{\abs{P}}{L} \hat{\lambda}_L \big( 1  + o_P(1)\big)  + \tfrac{\abs{D}}{L} \hat{\lambda}_L ( H + o_P(1) ) \\
&= \hat{\lambda}_L \left( \tfrac{\abs{P}}{L}  + \tfrac{\abs{D}}{L} H + o_P(1) \right).
\end{align*}
The proof follows since $\frac{\abs{P}}{L} \rightarrow p$ and $\frac{\abs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$.
\end{IEEEproof}

\begin{lemma}\label{lem:k2conv}
$k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) ).$
\end{lemma}
\begin{IEEEproof}
Since $\hat{\lambda}_L \in [-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ it is only the behaviour of the function $k_2(\lambda)$ for $\lambda\in [-\tfrac{\pi}{M}, \tfrac{\pi}{M})$ that is relevant.  We will analyse $k_2(\lambda)$ for non negative $\lambda$, i.e., when $0 \leq \lambda < \tfrac{\pi}{M}$.  An analagous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  To keep our notation clean put
\[
\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}.
\]
For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_k)$, then
\[
\fracpart{\Phi_1} = \Phi_1 - \round{\Phi_1} = \Phi_1 - \tfrac{2\pi}{M}k.
\]
Similarly, if $\Phi_1 \in  [\psi_{k-1}, \psi_{k} - \lambda)$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k,
\]
whilst, if $\Phi_1 \in [\psi_{k} - \lambda, \psi_{k})$, then
\[
\fracpart{\Phi_1 + \lambda} = \Phi_1 + \lambda - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}.
\]
So, when $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - &\sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k) - \sin(\Phi_1 - \tfrac{2\pi}{M}k),
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k)$ about $\Phi_1 - \tfrac{2\pi}{M}k$ we obtain 
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} &= \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k) + \zeta_k(\lambda)\big) \\
&= \lambda\big(\cos\fracpart{\Phi_1} + \zeta_k(\lambda)\big).
\end{align*}
where, for each integer $k$, the function $\zeta_k$ is continuous with $\zeta_k(0) = 0$.  Alternatively, when $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$,
\begin{align*}
\sin\fracpart{\lambda + \Phi_1} &- \sin\fracpart{\Phi_1} \\
&= \sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k)
\end{align*}
and by a Taylor expansion of $\sin(\lambda + \Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M})$ about $\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}$,
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&=  s_k(\Phi_1) + \lambda\big(\cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) + \zeta_{k+1}(\lambda)\big) 
\end{align*}
where
\[
s_k(\Phi_1) = \sin(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \sin(\Phi_1 - \tfrac{2\pi}{M}k).
\]
Putting,
\[
c_k(\Phi_1) = \cos(\Phi_1 - \tfrac{2\pi}{M}k - \tfrac{2\pi}{M}) - \cos(\Phi_1 - \tfrac{2\pi k}{M})
\]
we can write
\begin{align*}
\sin&\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \\
&= s_k(\Phi_1) + \lambda\big(\cos(\Phi_1 - \tfrac{2\pi k}{M}) + c_k(\Phi_1) + \zeta_{k+1}(\lambda)\big) \\
&= s_k(\Phi_1) + \lambda\big(\cos\fracpart{\Phi_1} + \eta_k(\lambda, \Phi_1) \big).
\end{align*}
where, for convenience, we have defined the function, 
\[
\eta_k(\lambda, \Phi_1) = c_k(\Phi_1) + \zeta_{k+1}(\lambda).
\]  
Observe that both $s_k$ and $c_k$ are continuous functions and that $s_k(\psi_{k}) = -2\sin(\tfrac{\pi}{M})$ and $c_k(\psi_{k}) = 0$.  %It follows, since $\zeta_{k+1}$ is also continuous, that the function $\eta_k(\lambda, \Phi_1)$ is continuous in both $\lambda$ and $\Phi_1$, and $\eta_k(0, \psi_k) = 0$.

Let us now collate what we have.  For each integer $k$, if $\Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda )$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} + \lambda\zeta_k(\lambda),
\]
whilst, if $\Phi_1 \in [ \psi_{k} - \lambda,\psi_{k})$, then
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda \cos\fracpart{\Phi_1} + s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1).
\]
Since the intervals $[\psi_{k-1}, \psi_{k})$ partion the real line, that is $\reals = \cup_{k\in\ints}[\psi_{k-1}, \psi_{k})$, then, for all $\Phi_1 \in \reals$,
\[
\sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} = \lambda\cos\fracpart{\Phi_1} +  v(\lambda, \Phi_1) 
\]
where $v(\lambda, \Phi_1) = \sum_{k\in\ints} v_k(\lambda, \Phi_1)$ and
\begin{equation}\label{eq:vk}
v_k(\lambda,\Phi_1) = \begin{cases}
s_k(\Phi_1) + \lambda\eta_k(\lambda, \Phi_1) &  \Phi_1 \in [ \psi_{k} - \lambda,\psi_{k} ) \\
\lambda\zeta_k(\lambda) & \Phi_1 \in [\psi_{k-1}, \psi_{k} - \lambda ) \\
0 & \text{otherwise}.
\end{cases}
\end{equation}
Now we can write,
\begin{align*}
k_2(\lambda) &=  \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big) \\
&= \expect R_1\big( \lambda\cos\fracpart{\Phi_1} + v(\lambda, \Phi_1)  \big) \\
&= \lambda h_2(0) + \expect R_1 v(\lambda, \Phi_1).
\end{align*}
Define the function $W(\lambda) = \expect R_1 v(\lambda, \Phi_1)$ so that $k_2(\lambda) = \lambda h_2(0) + W(\lambda).$  Lemma~\ref{lem:expRvlamphi} shows that $W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$, and
\[
H_1 = - 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\psi_k) = H - h_2(0).
\]
Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\gamma(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\gamma(\hat{\lambda}_L) = o_P(1)$, and therefore 
\[
k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( h_2(0) + H_1 + o_P(1) ) = \hat{\lambda}_L ( H + o_P(1) )
\]
as required.  It remains to prove Lemma~\ref{lem:expRvlamphi}.
\end{IEEEproof}
